Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-18 Ben_Manuscripts/transport/Draft.tex
Formatted solute table

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
  \begin{tabular}{ |lcclcc| }
    \hline
    Name & Abbreviation & Structure & Name & Abbreviation & Structure \\ \hline

	\color{blue}{Methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{blue}{Butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Propylene Glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{red}{Ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\
%    \hline
%    \end{tabular}
%    \end{minipage}%
%    
%    \begin{minipage}{.2\linewidth}
%    \tiny
%    \begin{tabular}{ | l c c | }
%    \hline
%    Name & Abbreviation & Structure \\ \hline
    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\

    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/methanol.png}
    \end{minipage} \\
    \hline
  \end{tabular}
%  \end{minipage}
  \caption{}\label{table:abbreviations}
  \end{table}

>>>>

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{Methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/URE.pdf}
    \end{minipage} \\

   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ETH.pdf}
    \end{minipage} &

    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACN.pdf}
    \end{minipage} \\

  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PR.pdf}
    \end{minipage} &

    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ATO.pdf}
    \end{minipage} \\

    \color{blue}{Butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/BUT.pdf}
    \end{minipage} &

    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/SOH.pdf}
    \end{minipage} \\

    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GCL.pdf}
    \end{minipage} &

    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMS.pdf}
    \end{minipage} \\

    \color{red}{Propylene Glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PG.pdf}
    \end{minipage} &

    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMP.pdf}
    \end{minipage} \\

    \color{red}{Glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GLY.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/THF.pdf}
    \end{minipage} \\

    \color{red}{Tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/TET.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMF.pdf}
    \end{minipage} \\

    \color{red}{Ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/RIB.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PCB.pdf}
    \end{minipage} \\

    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACH.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/EAC.pdf}
    \end{minipage} \\

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors corresponds to solute groupings
  and are used in many plots. Blue corresponds to simple alcohols, red to 
  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
  % BJC: achemso for jpcb makes table captions bold
  % BJC: also, it's published that way
  \end{table}
